%; /usr/bin/env xelatex -output-directory=.build -halt-on-error $0 && cp .build/*.pdf ./; exit

% Add 'print' as an option in the square bracket to remove colors from this template for printing
\documentclass[]{friggeri-cv}

% Reduce hyphens for better copy-paste and machine document scanning
\hyphenpenalty=1000

\begin{document}

\header{Mocy}{Sheng}{Software Designer}

% ----------------------------------------------------------------------------------------
% SIDEBAR SECTION
% ----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
  \section{Summary}
  A lava shadow as I
  A black elf
  with bright eyes
  \section{Contact}
  +1 (415) 741--7785
  \href{mailto:ranmocy+cv@gmail.com}{ranmocy@gmail.com}
  \href{https://ranmocy.me}{https://ranmocy.me}
  \href{https://www.linkedin.com/in/ranmocy}{ranmocy@linkedin}
  \href{https://github.com/ranmocy}{ranmocy@github}
  \href{https://twitter.com/ranmocy}{ranmocy@X}
  \section{Languages}
  English, Chinese
  Swift {\color{red} $\varheartsuit$}
  TypeScript \& React
  Java \& Kotlin \& Android
  Python
  C, Ruby, LaTeX
  \section{Interests}
  Philosophy
  Design
  Build
\end{aside}

% ----------------------------------------------------------------------------------------
% PROFESSIONAL SUMMARY SECTION
% ----------------------------------------------------------------------------------------

Mocy has 10+ years experiences building large-scale systems serving billions.
Expert in full-stack, mobile, ML, and cloud.
Proven leader launching products end-to-end with measurable impact.

% ----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
% ----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
  % ------------------------------------------------
  \entry{2024 --- Now}
  {Apple \emph{--- Senior Software Engineer}}
  {Sunnyvale, CA}
  {
    \emph{Apple Vision Pro}
    \begin{itemize}
      \item Attestation service:
      Developed a cryptography-backed data attestation service in Apple Cloud using Swift full-stack.
      Implemented end-to-end encryption, and zero-knowledge proofs for privacy-preserving verification.
      \item Computer Vision ML Model:
      Developed a ML model using PyTorch to automatically generate optimized 
      computer vision models for AR/VR applications.
      Processed 1TB+ training datasets using distributed pipelines.
      Replaced hours of training time with milliseconds of inferencing time.
    \end{itemize}
  }
  % ------------------------------------------------
  \entry{2022 --- 2024}
  {Narya AI \emph{--- Head of Engineering / Founding Engineer}}
  {Palo Alto, CA}
  {
    \emph{Narya.ai} is a no-code platform for testing and securing EVM-based smart contracts,
    fully supporting the Solidity programming language.

    Owned the entire product development, including software, machine learning, product, and UI, and led a team of 5.
    Launched the product from scratch to production.

    \begin{itemize}
      \item Developed a proprietary Rust-based fuzzing engine to find smart contract bugs,
      which are traditionally reviewed manually by smart contract auditors.
      Our engine runs faster and finds more bugs than popular competitors like Foundry or Echidna.
      \item LLM-based code generation to quickly create an interaction flow.
      \item For NFT projects, it can generate a complete set of tests within 10-30 minutes,
      significantly reducing the time required from days of an engineer's work.
    \end{itemize}
  }
  % ------------------------------------------------
  \entry{2015 --- 2022}
  {Google \emph{--- Senior Software Engineer}}
  {Mountain View, CA / Austin, TX}
  {
    \emph{Android Google Play Services} runs on 2B+ Android devices and has 100+ module teams contributing to it.

    \begin{itemize}
      \item Reworked Android components virtualization with code generation.
      Reduced maintenance overhead for 100+ module teams by enabling
      latest AndroidX usage with backward compatibility to the container app.
      \item Led and coordinated multiple teams across different PAs to
      safely enable Kotlin for all teams contributing to the app.
    \end{itemize}

    \emph{Family Link} provides parental supervision for Google accounts,
    serving millions of actively supervised Android devices.
    See \url{http://g.co/familylink}.

    Led a team of 4 engineers and was responsible for all parental supervision features on millions of kids' Android devices.

    \begin{itemize}
      % Complex work
      \item Reworked the rule-based Time Limit feature, the most critical and complex feature.
      This effort reduced negative user feedback by 90\%.
      % Reliablity
      \item Developed a policy-based framework to improve reliability.
      Defined all logging and metrics for all major features.
      Enabled feature-flag based A/B testing and quick debugging for all feature and APK releases.
      % Release
      \item Defined APK and feature release processes and policies with automated enforcement.
      Maintained compatibility for the app to run on all OS and the container app released in the past 10 years.
      \item Organized regular tech talks among large teams on how to work in the stack.
    \end{itemize}
  }
  % ------------------------------------------------
\end{entrylist}
\begin{entrylist}
  % ------------------------------------------------
  \entry{2014 Summer}
  {Twitter Ads \emph{--- Software Engineer Intern}}
  {San Francisco, CA}
  {
    Full-stack development with Ruby on Rails and Backbone.js.\@
    \begin{itemize}
      \item Tweet Preview: Send promoted tweet previews to advertisers.
      \item Performance profiling and optimization, improving Campaign Form page load time by 7.03\% at P99.
    \end{itemize}
  }
  % ------------------------------------------------
  \entry{2011 --- 2013}
  {GitCafe \emph{--- Full-stack Developer and System Administrator}}
  {Shanghai, China}
  {
    Full-stack development with Ruby on Rails.
    \begin{itemize}
      \item Designed and implemented the main Git hosting service, including Git servers, Wiki, Pages,
      Pull Requests, notifications, and account/billing management.
      \item Designed and implemented metrics system and optimized page loading time.
    \end{itemize}
  }
  % ------------------------------------------------
\end{entrylist}

% ----------------------------------------------------------------------------------------
% TOY SECTION
% ----------------------------------------------------------------------------------------

\section{Toys}

\begin{entrylist}
  % ------------------------------------------------
  \entry{Idid.Im}
  {I did, therefore I am}
  {JavaScript/React}
  {
    An app that helps to organize your life and to make it meaningful.\\
    Web: \url{https://idid.im}
  }
  % ------------------------------------------------
  \entry{Monkey Tree}
  {Fix phonetic names for Chinese contacts for sorting}
  {Java/Android}
  {
    A 4.8/5 stars app on PlayStore. Users love it.\\
    Android: \href{https://play.google.com/store/apps/details?id=me.ranmocy.monkeytree}{\texttt{market://details?id=me.ranmocy.monkeytree}}\\
    Source: \url{https://github.com/ranmocy/MonkeyTree}
  }
  % ------------------------------------------------
  \entry{SparkDriverLess}
  {A driver-less version of mini Spark}
  {Python}
  {
    Source: \url{https://github.com/ranmocy/SparkDriverLess}
  }
  % ------------------------------------------------
  \entry{Web-Stub}
  {Generates JSDoc and JavaScript stub from WebIDL}
  {JavaScript}
  {
    For IDE auto-completion and type checking.\\
    Source: \url{https://github.com/ranmocy/web-stub}
  }
  % ------------------------------------------------
  \entry{rCaltrain}
  {A Caltrain scheduler}
  {JavaScript/Android/iOS}
  {
    Web: \url{https://github.com/ranmocy/rCaltrain}\\
    Android: \href{https://play.google.com/store/apps/details?id=me.ranmocy.rcaltrain}{\texttt{market://details?id=me.ranmocy.rcaltrain}}
  }
  % ------------------------------------------------
  \entry{Guard-Rails}
  {Watch on your Rails and restart it as needed with Guard}
  {Ruby}
  {
    Maintainer: \url{https://github.com/ranmocy/guard-rails}
  }
  % ------------------------------------------------
\end{entrylist}

% ----------------------------------------------------------------------------------------
% EDUCATION SECTION
% ----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
  % ------------------------------------------------
  \entry{2013 --- 2015}
  {Master \textnormal{of Computer Science}}
  {University of San Francisco}
  {
    \emph{GPA:~3.95/4.0}: Algorithms, Artificial Intelligence, Theory of Computation
  }
  % ------------------------------------------------
  \entry{2009 --- 2013}
  {Bachelor \textnormal{of Mechanical Design}}
  {Shanghai Jiao Tong University}
  {
    \emph{Director}, \emph{Drama}, \emph{Crosstalk}, \emph{Movie}
  }
  % ------------------------------------------------
\end{entrylist}

% ----------------------------------------------------------------------------------------
% AWARDS SECTION
% ----------------------------------------------------------------------------------------

\section{Awards}

\begin{entrylist}
  % ------------------------------------------------
  \entry{2008}
  {NOIP 2008}
  {China Computer Federation}
  {\emph{First Prize} of National Olympiad in Informatics in Provinces}
  % ------------------------------------------------
  \entry{2007}
  {NOIP 2007}
  {China Computer Federation}
  {\emph{First Prize} of National Olympiad in Informatics in Provinces}
  % ------------------------------------------------
  \entry{2006}
  {NOIP 2006}
  {China Computer Federation}
  {\emph{First Prize} of National Olympiad in Informatics in Provinces}
  % ------------------------------------------------
\end{entrylist}

\end{document}
