%; /usr/bin/env mkdir -p .build && xelatex -output-directory=.build -halt-on-error $0 && cp .build/*.pdf ./; exit

% Add 'print' as an option in the square bracket to remove colors from this template for printing
\documentclass[]{friggeri-cv}

% Reduce hyphens for better copy-paste and machine document scanning
\hyphenpenalty=1000

\begin{document}

\header{Mocy}{Sheng}{Software Designer}

% ----------------------------------------------------------------------------------------
% SIDEBAR SECTION
% ----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
  \section{Summary}
  A lava shadow as I
  A black elf
  with bright eyes
  \section{Contact}
  +1 (415) 741--7785
  \href{mailto:ranmocy+cv@gmail.com}{ranmocy@gmail.com}
  \href{https://ranmocy.me}{https://ranmocy.me}
  \href{https://www.linkedin.com/in/ranmocy}{ranmocy@linkedin}
  \href{https://github.com/ranmocy}{ranmocy@github}
  \href{https://twitter.com/ranmocy}{ranmocy@X}
  \section{Languages}
  English, Chinese
  Swift {\color{red} $\varheartsuit$}
  TypeScript \& React
  Java \& Kotlin \& Android
  Python
  C, Ruby, LaTeX
  \section{Interests}
  Philosophy
  Design
  Build
\end{aside}

% ----------------------------------------------------------------------------------------
% PROFESSIONAL SUMMARY SECTION
% ----------------------------------------------------------------------------------------

% Mocy has 10+ years experiences building large-scale systems serving billions.
% Expert in full-stack, mobile, ML, and cloud.
% Proven leader launching products end-to-end with measurable impact.

% ----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
% ----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
  % ------------------------------------------------
  \entry{2024 --- Now}
  {Apple \emph{--- Senior Software Engineer}}
  {Sunnyvale, CA}
  {
    \emph{Apple Vision Pro}
    \begin{itemize}
      \item Attestation service:
      Built a cryptography-backed data attestation service using Swift-based full-stack from iOS to Apple Cloud.
      Implemented end-to-end encryption and zero-knowledge proofs for privacy-preserving verification.
      \item Computer Vision Machine Learning Model:
      Built a computer vision ML model using PyTorch to generate optimized ML models for AR/VR applications.
      Processed 1TB+ training datasets using distributed Python pipelines.
      Replaced hours of training time with milliseconds of inferencing time.
    \end{itemize}
  }
  % ------------------------------------------------
  \entry{2022 --- 2024}
  {Narya AI \emph{--- Head of Engineering / Founding Engineer}}
  {Palo Alto, CA}
  {
    \emph{Narya.ai} is a no-code platform for testing and securing EVM-based smart contracts,
    built with TypeScript, React, and Next.js, fully supporting Solidity.

    Owned the entire product development from scratch to production, including software, machine learning, product, and UI.

    Led a team of 5, including full-stack engineers, ML engineers, and designers.

    \begin{itemize}
      \item Built a proprietary fuzzing engine in Rust to find smart contract bugs,
      which are traditionally reviewed manually by human auditors.
      Our engine runs faster and finds more bugs than competitors like Foundry or Echidna.
      \item Implemented code generation using LLM and Python pipeline to create interaction flows with Solidity quickly.
      \item For NFT projects, the system generates complete test suites within 10-30 minutes,
      reducing engineering time from days to minutes.
    \end{itemize}

    \emph{Meson.fi} is a platform that enables users to swap stablecoins across 70+ different chains in minutes rather than hours.
    We helped them develop and launch the first public version.
    See https://meson.fi.

    Led a team of 4, including engineers and designers.

    \begin{itemize}
      \item Web UI:
      Built a website using React, allowing users to interact with the protocol directly with their crypto wallets,
      and monitoring their transactions.
      \item Liquidity Provider Service:
      Built a high reliability, low latency, non-blocking backend service using TypeScript and Node.js.
      It monitors on-chain transactions and settles swapping requests.
    \end{itemize}
  }
  % ------------------------------------------------
\end{entrylist}
\begin{entrylist}
  % ------------------------------------------------
  \entry{2015 --- 2022}
  {Google \emph{--- Senior Software Engineer}}
  {Mountain View, CA / Austin, TX}
  {
    \emph{Android Google Play Services} runs on 2B+ Android devices and has 100+ module teams contributing to it.

    \begin{itemize}
      \item Reworked Android components virtualization using Java code generation and annotation processing.
      Reduced maintenance overhead for 100+ module teams by enabling
      latest AndroidX usage with backward compatibility to the container app.
      \item Led and coordinated multiple teams across different PAs to
      safely enable Kotlin for all teams contributing to the app.
    \end{itemize}

    \emph{Family Link} provides parental supervision for Google accounts,
    serving millions of actively supervised Android devices.
    See \url{https://g.co/familylink}.

    Led a team of 4 engineers and was responsible for all parental supervision features on millions of kids' Android devices.

    \begin{itemize}
      % Complex work
      \item Reworked the rule-based Time Limit feature, the most critical and complex feature.
      This effort reduced negative user feedback by 90\%.
      % Reliablity
      \item Developed a policy-based framework to improve reliability.
      Defined and built all logging and metrics for all major features.
      Enabled feature-flag based A/B testing and quick debugging for all feature and APK releases.
      % Release
      \item Defined APK and feature release processes and policies with automated enforcement.
      Maintained compatibility for the app to run on all OS and the container app released in the past 10 years.
      \item Organized regular tech talks among large teams on how to work in the stack.
    \end{itemize}
  }
  % ------------------------------------------------
  \entry{2014 Summer}
  {Twitter Ads \emph{--- Software Engineer Intern}}
  {San Francisco, CA}
  {
    Full-stack development using Ruby on Rails backend and Backbone.js frontend.
    \begin{itemize}
      \item Tweet Preview: Built promoted tweet preview feature for advertisers.
      \item Performance profiling and optimization, improving Campaign Form page load time by 7\% at P99.
    \end{itemize}
  }
  % ------------------------------------------------
  \entry{2011 --- 2013}
  {GitCafe \emph{--- Full-stack Developer and System Administrator}}
  {Shanghai, China}
  {
    Full-stack development using Ruby on Rails.
    \begin{itemize}
      \item Designed and implemented the main Git hosting service, including Git servers, Wiki, Pages,
      Pull Requests, notifications, and account/billing management.
      \item Built the metrics system and optimized the page loading time with proper caching strategies.
    \end{itemize}
  }
  % ------------------------------------------------
\end{entrylist}

\pagebreak

% ----------------------------------------------------------------------------------------
% TOY SECTION
% ----------------------------------------------------------------------------------------

\section{Toys}

\begin{entrylist}
  % ------------------------------------------------
  \entry{Idid.Im}
  {I did, therefore I am}
  {JavaScript/React}
  {
    An app that helps to organize your life and to make it meaningful.\\
    Web: https://idid.im
  }
  % ------------------------------------------------
  \entry{Monkey Tree}
  {Fix phonetic names for Chinese contacts for sorting}
  {Java/Android}
  {
    A 4.8/5 stars app on PlayStore. Users love it.\\
    Android: \href{https://play.google.com/store/apps/details?id=me.ranmocy.monkeytree}{\texttt{market://details?id=me.ranmocy.monkeytree}}\\
    Source: \url{https://github.com/ranmocy/MonkeyTree}
  }
  % ------------------------------------------------
  \entry{SparkDriverLess}
  {A driver-less version of mini Spark}
  {Python}
  {
    Source: \url{https://github.com/ranmocy/SparkDriverLess}
  }
  % ------------------------------------------------
  \entry{Web-Stub}
  {Generates JSDoc and JavaScript stub from WebIDL}
  {JavaScript}
  {
    For IDE auto-completion and type checking.\\
    Source: \url{https://github.com/ranmocy/web-stub}
  }
  % ------------------------------------------------
  \entry{rCaltrain}
  {A Caltrain scheduler}
  {JavaScript/Android/iOS}
  {
    Web: \url{https://github.com/ranmocy/rCaltrain}
  }
  % ------------------------------------------------
  \entry{Guard-Rails}
  {Watch on your Rails and restart it as needed with Guard}
  {Ruby}
  {
    Maintainer: \url{https://github.com/ranmocy/guard-rails}
  }
  % ------------------------------------------------
\end{entrylist}

% ----------------------------------------------------------------------------------------
% EDUCATION SECTION
% ----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
  % ------------------------------------------------
  \entry{2013 --- 2015}
  {Master \textnormal{of Computer Science}}
  {University of San Francisco}
  {
    \emph{GPA:~3.95/4.0}: Algorithms, Artificial Intelligence, Theory of Computation
  }
  % ------------------------------------------------
  \entry{2009 --- 2013}
  {Bachelor \textnormal{of Mechanical Engineering}}
  {Shanghai Jiao Tong University}
  {
    Mechanical Design
  }
  % ------------------------------------------------
\end{entrylist}

% ----------------------------------------------------------------------------------------
% AWARDS SECTION
% ----------------------------------------------------------------------------------------

\section{Awards}

\begin{entrylist}
  % ------------------------------------------------
  \entry{2008}
  {NOIP 2008}
  {China Computer Federation}
  {\emph{First Prize} of National Olympiad in Informatics in Provinces}
  % ------------------------------------------------
  \entry{2007}
  {NOIP 2007}
  {China Computer Federation}
  {\emph{First Prize} of National Olympiad in Informatics in Provinces}
  % ------------------------------------------------
  \entry{2006}
  {NOIP 2006}
  {China Computer Federation}
  {\emph{First Prize} of National Olympiad in Informatics in Provinces}
  % ------------------------------------------------
\end{entrylist}

\end{document}
